\section{Conclusion}
\subsubsection*{Performance summerization}
Following are a summarize of our work.
\begin{table}[h]
    \centering
    \begin{tabular}{|c|c|c|c|c|}
    \hline
    Model & Preprocess & Other Technique & Stage1 & Stage2 \\ \hline\hline
    KNN   & Diff \& Ratio   & None & 0.56786 & 0.54166  \\ \hline
    Linear Regression & TA \& Diff \& Ratio & None & 0.58147 & 0.5482 \\ \hline
    Logistic Regression & None & None & 0.571 & 0.5385 \\ \hline
    SVM & TA & Bl \& Ba \& Op & 0.57887 & 0.53349 \\ \hline
    SVM (Linear) & TA & GS & 0.57142 & 0.50980 \\ \hline
    SVM (RBF) & TA & GS & 0.57110 & 0.54656 \\ \hline
    Random Forest & None & None & 0.58989 & 0.5245 \\ \hline
    XGboost & TA & Op & 0.57725 & 0.54166 \\ \hline
    CATboost & DSS & Op & 0.57985 & 0.54493 \\ \hline
    \end{tabular}
    \label{tab:example_table}
\end{table}\\
% \subsubsection*{Abbreviation}
Corresponding Abbreviation : \\
(TA : Team Attribute), (DSS : Drop std and skew ), (GS : Grid Search), (Bl : Blending),\\
 (Ba : Bagging), (Op : Optuna).
% \begin{itemize}
%     \item[TA] Team Attribute
%     \item[DSS] Drop std and skew 
%     \item[GS] Grid Search
%     \item[Bl] Blending
%     \item[Ba] Bagging
%     \item[Op] Optuna  
% \end{itemize}

\subsection*{Model Selection and Result Analysis}
\par We suggest that you should use our Random Forest model for same season prediction and our Linear Regression model for stage2. 
\par Noted that we have done Diff \& Ratio Technique on our data in the Linear Regression model. This give a inspire that using our Diff \& Ratio pre process, we can make data more linear separable (given that Linear SVM that only do Team Attribute preprocess doesn't give a as well result). 
\par We also found that using the validation cutting strategy we've used in CATboost(we call it date strategy since it cut validation data by date) with a parameter searching algorithm (such as Optuna) can give a better result than random validation strategy.

\subsection*{Future Improvement}
\par In some of our model, we didn't use Optuna to search for best parameter due to the limit of time and  computing resources. However, this will definitely give us a better result. 
\par Further more, we should use date strategy to decide our validation data and use that to do parameter search. This may make our model better at a specific task like same season prediction or new season prediction.
\par In the future, we should also consider use Diff \& Ratio preprocess on more model. Specifically, we should definitely try it on Linear SVM since it gives a good linear separable property. 